Increasing the topological gap by an order of magnitude through the geometry for Majorana SNS junctions.

### 2019-02-05 paper/snakemajoranas.tex
review on phone

\comment{The phase diagram does not change much, except we see a cleaner spectrum as a result of the D class symmetry. }
Similar to what is described by Pientka et. al~\cite{pientka2017topological}, we see that the ribbon topology has a diamond-like structure as a function of phase $\phi$ and Zeeman field $E_Z$.
We also observe additional gap closings which are due to the BDI symmetry that is present.
As expected for the zigzag system, the magnitude of the gap is significantly improved, while maintaining the diamond-like shape.
As the zigzag shape destroys the additional symmetry, moving it to class D, we see a cleaner topological region.

\begin{figure}[!htb]
\includegraphics[width=0.95\columnwidth]{figures/bandstructures}
\caption{Figure of the bandstuctures.
Where the lines are (blue) $\phi=0$, $B=0$ and (red) $\phi=\pi$, $B \ne 0$.
and the subplots (a) $z_y=0$, (b) $z_y=\frac{W}{4}$, and (c) $z_y=\frac{W}{2}$, where $W$ is the junction width.
We observe that once there are no more straight trajectories inside the junction (when $z_y=\frac{W}{2}$) the spectrum becomes most insensitive to the momentum $k_x$.
\label{fig:bandstuctures}}
\end{figure}

\begin{figure}[!htb]
\includegraphics[width=0.95\columnwidth]{figures/phasediagrams}
\caption{Phase diagrams of a straight system (a, b) and zigzag system (c, d), where (a, c) are $E(\mu, B)$ and (b, d) are $E(\phi, B)$.
We use a generalized eigenvalue problem to find all phase boundaries at once and find the minimal energy gap by finding the minimum in the spectrum: $\min{E(k)}$.
\label{fig:phasediagrams}}
\end{figure}

@@

\comment{In a zigzag geometry Majoranas are localized within one segment of zigzag.}

>>>>

\comment{The phase diagram does not change much, except we see a cleaner spectrum as a result of the D class symmetry. }
Similar to what is described by Pientka et. al~\cite{pientka2017topological}, we see that the ribbon topology has a diamond-like shape as a function of phase $\phi$ and Zeeman field $E_Z$.
We also observe additional gap closings which are due to the BDI symmetry that is present.
As expected for the zigzag system, the magnitude of the gap is significantly improved, while preserving the diamond-like shape in parameter space.
Because the introduction of the zigzag shape moves the system to class D, we see a cleaner topological region due to the absence of the gap closings resulting from the BDI symmetry.

\begin{figure}[!htb]
\includegraphics[width=0.95\columnwidth]{figures/bandstructures}
\caption{Figure of the bandstuctures.
Where the lines are (blue) $\phi=0$, $B=0$ and (red) $\phi=\pi$, $B \ne 0$.
and the subplots (a) $z_y=0$, (b) $z_y=\frac{W}{4}$, and (c) $z_y=\frac{W}{2}$, where $W$ is the junction width.
We observe that once there are no more straight trajectories possible inside the junction (when $z_y=\frac{W}{2}$) the spectrum becomes most insensitive to the momentum $k_x$.
\label{fig:bandstuctures}}
\end{figure}

\begin{figure}[!htb]
\includegraphics[width=0.95\columnwidth]{figures/phasediagrams}
\caption{Phase diagrams of a straight system (a), (b) and zigzag system (c), (d), where (a), (c) are $E(\mu, B)$ and (b), (d) are $E(\phi, B)$.
% We use a generalized eigenvalue problem to find all phase boundaries at once and find the minimal energy gap by finding the minimum in the spectrum: $\min{E(k)}$.
\label{fig:phasediagrams}}
\end{figure}

@@

\comment{In a straight system, the Majoranas are very poorly localized.}
For the ribbon system [Fig.~\ref{fig:wavefunction}(a)], we see that the decay of the density is long compared to the system size.
The wavefunction extends to the center of the system, resulting in overlapping Majoranas and a non-zero energy of the state.
Further, the energy of the Majorana state in the straight system is badly septated from the next lowest lying eigenstate.
Altogether, for the parameters of the system, the Majoranas are very poorly localized and topological protection against perturbations is minimal.

\comment{In a zigzag geometry Majoranas are localized within one segment of zigzag.}
All of the zigzag type geometries show a reduced coherence length.
The delocalized nature of the wavefunctions is clearly visible through the density plots.
Quantitatively, the improvement in the localization of the Majoranas is also distinctly apparent: the energies of the Majorana states are three orders of magnitude lower than the energy of the second lowest-lying wavefunctions.
As mentioned in the previous section, this can be attributed to the way the gap and velocity factor into the Majorana coherence length.

\comment{We also confirm that the specific shape does not matter.}
The shape of the wavefunctions does not change significantly depending on the details of the geometry.
The sharp corners of the sawtooth versus the smooth shape of the snakelike system do not have a significant impact on the shape of the wavefunction and neither do the disordered edges effect the relevant parameters.
